\bf Faster Neural Machine Translation Inference

### 2018-05-11 fast-beam/fast-beam.tex
use requireProb

Thirdly, the calculation of $max$ and $sum$ can be done in one loop by adjusting $sum$ whenever a higher $max$ is found, Equation~`.
\begin{eqnarray*}
sum & = & e^{a - max_b} + e^{b - max_b} \\
    & = & e^{a - max_a + \Delta} + e^{b - max_b} \\
    & = & e^{\Delta} e^{a - max_a} + e^{b - max_b}
\end{eqnarray*}
where $\Delta = max_a - max_b$ and $max_b > max_a$. The outline of the our function is shown in Algorithm~\ref{algo:Fused Kernel}.

In fact, a well known optimization is to skip the softmax operation altogether and calculate the argmax over the input vector, Algorithm~\ref{algo:Argmax only}. This is only possible for beam size 1 and when we are not interested in returning the softmax probabilities.

@@

This changes does not reduce the asymtotic runtime of our algorithm which remains at $\mathcal{O}(|p|)$, it brings the number of iterations over $p$ down from 5 to 1. In practise, this has a significant affect on inference speed.

>>>>

Thirdly, the calculation of $max$ and $sum$ can be done in one loop by adjusting $sum$ whenever a higher $max$ is found:
\begin{eqnarray*}
sum & = & e^{a - max_b} + e^{b - max_b} \\
    & = & e^{a - max_a + \Delta} + e^{b - max_b} \\
    & = & e^{\Delta} e^{a - max_a} + e^{b - max_b}
\end{eqnarray*}
where $\Delta = max_a - max_b$ and $max_b > max_a$. The outline of our function is shown in Algorithm~\ref{algo:Fused Kernel}.

In fact, a well known optimization is to skip softmax altogether and calculate the argmax over the input vector, Algorithm~\ref{algo:Argmax only}. This is only possible for beam size 1 and when we are not interested in returning the softmax probabilities.

@@

These changes do not reduce the asymtotic runtime of our algorithm, which remains at $\mathcal{O}(|p|)$, but it does bring the number of iterations over $p$ down from 5 to 1. In practise, this has a significant affect on inference speed.
